Manuscript

### 2014-09-03 inst/simulation/manuscript.Rmd
...

```{r figure-3}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)

p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) + stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") + facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
```

>>>>

```{r figure-3-init}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)

meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
  data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
})
logPopulationSizes <- populationSizes
logPopulationSizes$Observed <- log10(logPopulationSizes$Observed + 1)
logPopulationSizes$Estimated <- log10(logPopulationSizes$Estimated + 1)
logMeanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
  data.frame(True=mean(log10(x$Observed+1)), Estimated=mean(log10(x$Estimated+1)), Scenario=x$scenario)
})
```

```{r figure-3a}
p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") +
  geom_point(data=meanPopulationSizes, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3a.png", width=8, height=4)
```

```{r figure-3b}
p <- ggplot(logPopulationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") + 
  geom_point(data=logMeanPopulationSizes, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3b.png", width=8, height=4)
```

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
meanPopulationSizes
```
